Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-30 journal/article.tex
T: Coaching

Why is coaching used?

Coaches are who?

Who receives coaching --> Teams, very few cases with some other roles

How is coaching done?

% Coaching was a typical way for steering the agile adoption.
% What
In addition to training, a coaching approach was usually used to teach how to
work in an agile environment. As agile lacks rigorous prescriptions and builds
on human interactions, it is best learned in practical situations while a coach
is giving direction.
The main task of coaches was to guide development teams in their daily work.
Some cases described that roles such as the product owner or scrum master
received specialized coaching [P33, P52].
In addition to helping teams, coaches were driving the agile push [P2, P36,
P49], and advocated agile methods in general [P45].

@@

% How coaching evolves
As the agile way of working penetrated the organization the need for coaching
was decreasing, and coaching could be reduced [P18, P36]. However, some cases
described that the demand for coaching became permanent in order to keep the
development model healthy and to continuously pursue improvement [P6, P23].
Silva and Doss [P47] describe that internal coaches were required for making the
change grow. Over time the arrangement shifted from having external consultants
as coaches to creating an internal coaching community.

Some cases presented building of a coach community as an integral part of the
agile adoption [P6, P23, P32, P47].

To be able to coach efficiently it was required that the coach had detailed
understanding of the company's processes and systems [P23, P39].

The maturity of coaches grew over time [P32].

@@

[P1, P2]
* Why: best for introducing agile methods
* Why: They drive the push
* How: Coach in the team

[P3]
* Why: The change leader persuaded to introduce coaching
* Coach: The change leader
* Who: teams
* How: Teams were coached

[P6]
* Why: It helps to have people with experience
* Coach: An internal change leader, a team of coaches
* Who: Teams
* How: Start heavy a kick-off, and later draw back
* Particular: There were little coaches at start
* Particular: The coaches showed positive results, and management was convinced to invest in coaching

[P8]
* Why: Intensive coaching is necessary 4-6 months at start

[P9]
* Coach: A hired consultant specialist
* How: The coach embodied the best agile principles

[P16]
* Why: To ensure transformation is successful
* Coach: The cross-functional rollout team

[P18]
* Coach: An agile consultant
* When: For over a year
* How: Accompanied the introduction for over a year, trained on specific agile practices

[P23]
* Coaches: In-house coaching team, some external coaches
* The coach community needed to be tended to specifically
* If there were too few coaches things did not work
* Pair coaching, apprentice coaching
* Particular: The coaches needed to have specific knowledge of the company's systems and processes
* Particular: Coaches in pairs --> training of coaches
* Particular: Focus on coaching

[P27]
* Coaches: External coaches
* How: Train on agile practices

[P29]
* Coaches: Agile consultants
* Why: Having a impartial third party was a key success factor
--
* Coaches: The pilot team, matured teams
* Who: Teams
* How: Helping other teams in getting started
* How: Taking a formal mentoring role when it is required

[P33]
* Who: Product owners
* Why: Crucial to make it successful
* Particular: Coaches were brought in after the start of the transformation, when trouble already existed

[P36]
* Coaches: Coaches from a subcontractor
* How: The coaches drive the project
* How: Mentor in-house leads to take lead as soon as possible
* How: Retrospect and adapt
* When: The need for coaches disappeared gradually
* The coach role was apparently seen as the lead of the project

[P39]
* Coach: External support, hired Chief Scrum masters
* How: inspect and adapt
* Particular: Internal coaches had better understanding of the company's procedures

[P40]
* Who: Teams
* How: Coaching breakout sessions

[P41]
* Coach: Internal and external
* Who: Teams
* How: Coaching office hours
* How: Have a forum where teams can ask for help, and to share their implementation
* Particular: It was disliked to have peers as coaches, as they were not considered more knowledgeable

[P45]
* Coach: Internal small expert team
* Who: Teams
* How: Supporting, advocating agile development
* How: Educate and support teams interested in Scrum
* Particular: Later offering possibility to teach more Scrum mentors

[P46]
* The pilot teams were coached
* Who: Teams that are about to start agile projects
* How: A productized training workshop, and a jump start afterwards
* How: Key team roles are coached in the start, so that the start is successful

[P47]
* Why: The agile adoption required coaches
* Coaches: Initially external consultants
* Coaches: Internal people started taking coach positions
* Coaches: Apprentice coaches, guided by external experts
* Particular: A structure was created around coach certification
* Particular: A coach community

[P50]
* Coaches: Internal key roles, these received initial coach and role specific training
* When: When teams were starting
* How: Coached to facilitate start up of teams

[P52]
* Who: Paired line manager and Scrum master
* How: Pair coaching the pair itself
* Coach: In some cases an experienced Scrum master was brought to help the pair

% Inhouse coaching

What?

Why?

Benefits?

Differences?

[P2]
* Why: There were too few coaches, so new ones were trained internally

[P3]
* Benefit: The internal coaches were accessible. You could easily acquire coaching for your team

[P6]
* What: There is a train the trainer program
* Why: Coaches can be expensive, more coaches can scale up agile more quickly

[P9]
* There was a lack of qualified coaches
* Why: hiring good external coaches was difficult
* It was hard to make the internal coaching resources work as well

[P11]
* Coaches: The Scrum masters served as internal coaches

[P16]
* Coaches: The roll-out team coached

[P23]
* A coach community evolved
* Why: The organization was so large
* How: Paired coaching

[P31]
* A certain person was hiread as senior agile coach, and he stayed through out the transformation
* Coach: A person was hired permanently

[P32]
* Particular: The maturity of coaches grew over time
* Why: There were so many people to educate

[P39]
* Benefit: Internal coaches had understanding of procedures and communication policies

[P45]
* What: After 8 months the coaches started training future Scrum mentors

[P47]
* Why: There was an internal need. It just was necessary to have coaches.
* How: First there were some external coaches, then an internal community was built
* Coaches: People who were passionate to teach agile

[P49]
* Why: To scale up agile implementation
* Why: The internal coaches create the change

>>>>

% What
In addition to training, a coaching approach was usually used to teach how to
work in an agile environment. As agile lacks rigorous prescriptions and builds
on human interactions, it is best learned in practical situations while a coach
is giving direction.
The main task of coaches was to guide development teams in their daily work.
Some cases described that roles such as the product owner or scrum master
received specialized coaching [P33, P52].
In addition to helping teams, coaches were driving the agile push [P2, P36,
P49], and advocated agile methods in general [P45].

@@

% How coaching evolves
As the agile way of working penetrated the organization the need for coaching
was decreasing, and coaching could be reduced [P18, P36]. However, some cases
described that the demand for coaching had become permanent in order to keep the
development model healthy and to continuously pursue improvement [P6, P23].
The maturity of coaches was described to grow over time, as the agile
transformation progressed [P32].

% Internal coaching
The coaching positions were most often held by internal staff.
Internal coaches were required for making the change grow, and to scale up the
agile implementation [P47, P49]. Internal coaches had also the benefit of
understanding of the company's processes and systems [P23, P39], and teams were
able to access them easily [P3, P41]. Some cases presented building of a coach
community as an integral part of the agile adoption [P6, P23, P32, P47].

@@
